Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-07-21 document/ms.tex
Edits from Greg Herczeg now directly included in main manuscript

The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{2013PASP..125..306F}.  The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations expected among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.  The practical effect of this switch is that we obtain unique stellar parameter estimates $\vT_{o}$ for each spectral order $o$, whereas the \iancze strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.  We combine the $N_{\rm ord}$ sets of inferences on $\vT_{o}$ with heuristics like taking the weighted average of point estimates of parameter distributions of the most reliable subsets of orders.  We assume that these lossy heuristics offer a regression to the mean with a large number of spectral orders.

\section{Observations and data mining}\label{sec:obs}

\subsection{IGRINS Spectroscopy}\label{sec:igrins} 
We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{2014SPIE.9147E..1DP,2012SPIE.8450E..2SG} on the Harlan J. Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.  IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.  The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-band$.  The data were reduced with the Pipeline Package\footnote{\url{https://github.com/igrins/plp}}.  We performed telluric correction by dividing the spectrum of \name by an A0V star observed near-contemporaneously at similar air-mass.  The broad hydrogen lines in the A0V star produced broad flux excesses in the spectrum of \name.  No effort was made to remove these flux excesses, which affect several spectral orders. 
%List the spectral orders these lines affect.

\subsection{ESPaDOnS Spectroscopy}
We retrieved twelve existing ESPaDOnS spectra from \citet{2014MNRAS.444.3220D}.
\todo{Say some more about the spectra- what wavelength range used, chunking.}

\subsection{Photometric monitoring from ASASSN and \citet{grankin08}}

We retrieved $V-$band monitoring from the ASASSN survey \citep{2014ApJ...788...48S}.  This data covered 2012 January - 2016 March.  The 777 raw data points included near-contemporaneous measurements from repeated observations during the same visits, which lasted typically $<10$ minutes.  We grouped datapoints by these visits yielding 186 data points, assigning a mean value and standard deviation when there was more than 1 observation per visit, enforcing a floor uncertainty of 0.01, the native quoted uncertainty of the data points.  We assigned the native uncertainty of 0.01 when there was only a single observation per visit.

We also retrieved $V-$band monitoring from \citet{grankin08} which covers 1992 August - 2004 October with 284 data points.  Of those, 278 have $B-V$, 268 have $V-R$, and 18 have $U-B$.  We also compiled the 10 additional $V-$band photometric data points provided in \citet{2014MNRAS.444.3220D}.

Figure \ref{fig:PhotTime} assembles the \citet{grankin08}, \citet{2014MNRAS.444.3220D}, and ASASSN $V-$band monitoring plotted over the interval 1992-2016.  The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
	\vspace{-100mm}
	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
	\label{fig:lores}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
	\vspace{-100mm}
	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
	\label{fig:lores}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/tiovar} 
	\vspace{-100mm}
	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).  The V-band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.  The main panel shows a correlation between V-band magnitude and the TiO-7140 index, while the inset shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
	\label{fig:tiovar}
\end{figure*}

@@

>>>>

The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{foreman13}.  The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations expected among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.  The practical effect of this switch is that we obtain unique stellar parameter estimates $\vT_{o}$ for each spectral order $o$, whereas the \iancze strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.  We combine the $N_{\rm ord}$ sets of inferences on $\vT_{o}$ with heuristics like taking the weighted average of point estimates of parameter distributions of the most reliable subsets of orders.  We assume that these lossy heuristics offer a regression to the mean with a large number of spectral orders.

\section{Observations}\label{sec:obs}

\subsection{IGRINS Spectroscopy}\label{sec:igrins} 
We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{park14,gully12} on the Harlan J. Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.  IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.  The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-band$.  The data were reduced with the Pipeline Package\footnote{\url{https://github.com/igrins/plp}}.  We performed telluric correction by dividing the spectrum of \name by an A0V star observed near-contemporaneously at similar air-mass.  The broad hydrogen lines in the A0V star produced broad flux excesses in the spectrum of \name.  No effort was made to remove these flux excesses, which affect several spectral orders. 
%List the spectral orders these lines affect.

\subsection{ESPaDOnS Spectroscopy}
We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MATYSSE Large Program.  These spectra cover 3900-10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.  The Zeeman Doppler Imaging obtained from these observations were analyzed by \citet{donati14}.  In this paper we concentrate on the intensity spectrum.

Chunking, estimate flux calibration...

\subsection{Low-resolution optical and near-IR spectra}

Palomar/DBSP \citep{herczeg14}

APO/TripleSpec (Covey)

\subsection{Photometric monitoring from ASAS-SN and \citet{grankin08}}

We retrieved $V-$band monitoring from the ASAS-SN survey \citep{shappee14}, obtained from 2012 January -- 2016 March in 186 visits.
We also retrieved optical photometry of \name\ obtained in 284 visits in $V$-band (278 with $B$ and 268 with $R$ from 1992 August - 2004 October \citep{grankin08}, and 10 additional $BVR$ epochs obtained by \citet{donati14}.   Figure \ref{fig:PhotTime} assembles the \citet{grankin08}, \citet{donati14}, and ASAS-SN $V-$band monitoring plotted over the interval 1992-2016.  The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.

%The 777 raw data points included near-contemporaneous measurements from repeated observations during the same visits, which lasted typically $<10$ minutes.  We group these near-simultaneous observations by assigning 
% datapoints by these visits yielding 186 data points, assigning a mean value and standard deviation when there was more than 1 observation per visit, enforcing a floor uncertainty of 0.01, the native quoted uncertainty of the data points.  We assigned the native uncertainty of 0.01 when there was only a single observation per visit.

@@

\begin{figure*}
    	\vspace{-60mm}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
	\vspace{-100mm}
	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
	\label{fig:lores}
\end{figure*}

@@

\begin{figure*}
	\centering
	\vspace{-60mm}
	\includegraphics[width=0.95\textwidth]{figures/lkca4_tio_forpaper} 
    	\vspace{-30mm}
	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).  The V-band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.  The main panel shows a correlation between V-band magnitude and the TiO-7140 index, while the inset shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
	\label{fig:tiovar}
\end{figure*}

@@

\begin{table}
\begin{tabular}{lccccc}
Method & $T_{eff}$ & $A_V$ & $M$ & $\log$ Age \\
\hline
Blue, high resolution & 4100 & 0.68 \\
Low resolution optical & 3670 & 0.35 & \\
\hline
\multicolumn{5}{c}{Simulated}
GAIA-ESO\\
APOGEE \\
\hline
This work & 3525 & \\
\hline
\end{tabular}
\end{table}

\subsection{Placing LkCa 4 on an HR Diagram}

\begin{figure}
	\centering
    	\vspace{-30mm}
	\includegraphics[width=0.95\textwidth]{figures/lkca4_hrdiag}
    	\vspace{-30mm}
	\caption{Placeholder for HR Diagram Figure}
	\label{fig:hrdiag}
\end{figure}

The spectrum of LkCa 4 is well reproduced by a cool component of $3000$ K covering 75\% of the surface and a $4200$ K component covering 25\% of the surface.  The effective temperature of these two components is 3525 K, based on the average surface flux.  Decreasing the cool spot size to 60\% would increase the effective temperature to 3670 K, while increasing the spot size to 85\% would decrease the effective temperature to 3370 K.  {\bf GJH note:  holy crap!!!}  Scaling our composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming a distance of 131 pc based the parallax distance of the nearest Taurus member \citep{torres12}.

This improved characterization of LkCa 4 should lead to more accurate estimates of mass and age from pre-main sequence tracks.  However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models.  This age is uncomfortably young.  LkCa 4 is not located deeply within a molecular cloud and is not associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.  The inferred age and low mass may instead be evidence that strong magnetic fields are inhibiting convection and slowing the contraction rate.

Comparisons to other results (both real and simulated):  APOGEE, GAIA-ESO,
